prep_annotating

### 2022-10-13 code/prep_annotate.Rmd
do sbert on post-quiz names

>>>>

# Sbert prep on end stuff

```{r}
library(jsonlite)

ParseJSONColumn <- function(x) {
  str_c("[ ", str_c(x, collapse = ",", sep=" "), " ]")  %>% 
    fromJSON(flatten = T)
}
d.players <- read_csv(here(paste(read_data_path, "players.csv", sep = "")),
                      col_types = cols()) %>% distinct() |> 
  select(playerId,own=flower_labels,other=otherflower_labels) |> 
  inner_join(d.rounds.final |> select(gameId, playerId, conditionName, color) |> unique()) |> 
  mutate(own= ifelse(is.na(own), '{}', own)) %>%
  mutate(other = ifelse(is.na(other), '{}', other)) %>%
  mutate(own = map(own, .f = ParseJSONColumn)) %>% 
  mutate(other =  map(other, .f = ParseJSONColumn)) %>% 
  unnest(cols=c(own,other), names_sep=":") %>% 
  pivot_longer(cols=starts_with("own")|starts_with("other")) %>% 
  filter(!is.na(value)) %>% 
  filter(value!="") %>% 
  separate(name, into=c("seen","color","num")) %>% 
  rename(text=value) %>% 
  mutate(text = gsub("[/?/.]", ' ', text),
         text = str_squish(text),
         utt_length_chars = str_length(text), 
         utt_length_words = str_count(text, "\\W+") + 1) |> write_csv(here(annotation_path,"post_test.csv"))

```{r, include=F, eval=F}
library(reticulate)
np <- import("numpy")
mat = np$load(here(annotation_path,'post_sbert_post_test.npy'))
saveRDS(mat,here(annotation_path,'post_sbert_post_test.RData'))
```
